### 2018-01-17 Documents/bootcamp_topic_intro.tex
Intro Outline Update, move to jupyter

\section*{\href{https://atom.io/}{Atom}}
\begin{itemize}
\item A versatile, text editor. Must have tool for serious work.
\item We will use it to open files, look at them, learn some markdown.
\item Lets install it
\begin{itemize}
\item Put red sticker on your laptop
\item Google ``atom download'' or borrow a USB drive
\item Download or copy installer to your computer
\item Run installer
\item Start Atom
\item Replace red sticker with green when Atom opens
\end{itemize}
\item Go and open new file
\item type ``my first file'', then comma, then birth year, then comma, high school graduation year, then comma, college graduation year (or expected graduation year). For me it looks like this\\
    \\
{\tt my first file, 1978, 1996, 2001} 
\item Save as: \verb|my_first_file.csv| in your \verb|Data_Bootcamp| file.
\item \textbf{Pro tip: naming convention and file type is important in this course}
\end{itemize}

\section*{\href{https://github.com}{GitHub}}
\begin{itemize}
\item What I will use it for\ldots
\begin{itemize}
\item Source of ALL course materials
\item Place for you to grab materials on the fly. Save files by cut and paste, clever save as, or "Raw" (ask about this)
\end{itemize}
\item You need to create an account and email me your username
\item What you will use it for\ldots
\begin{itemize}
\item Post your homework and projects; I will ``pull'' them from there.
\item Long run: Think of this like an artists portfolio. Here you can post your code and projects and show potential employers, family, friends what you have done.
\end{itemize}
\item Now lets use it
\begin{itemize}
\item Put red sticker on your laptop
\item Sign into github (if you do not have an account, create one)
\item Create a new repository and name it \verb|my_first_repository|,
\item place the \verb|my_first_file.csv| file you created in it,
\item Great job! Replace red sticker with green!\\
Next class, I'm going to try and ``pull'' the file and then report some statistics about the class to you.
\end{itemize}
\end{itemize}

@@

\item Environments
\begin{itemize}
\item Environments?  (Analogy:  Word is an environment for creating Word docs.)
\item Spyder:  classic coding environment with editor and output windows
\item Jupyter:  environment for creating IPython notebooks, which combine code with text and output
\end{itemize}
\end{itemize}

@@

\needspace{2\baselineskip}
\item Run test program in Spyder
\begin{itemize}
\item Put red sticker on your laptop
\item From Launcher, launch Spyder (labelled ``spyder-app'')
\item Look around (editor, IPython console, Object inspector)
\item Enter test program in editor (on the left)
\item Save in \verb|Data_Bootcamp| directory as \verb|bootcamp_test.py|
(File, Save as, look for folder)
\item Run program (click on large green triangle)
\item Look for correct output (last line should be {\tt 3.6.x etc})
\item Switch to green sticker if it works
\end{itemize}

@@

\item Spyder startup summary
\begin{itemize}
\item Open by typing Launcher in search box (spotlight on Macs), then choose spyder-app.
\item Or just type Spyder in search box
\end{itemize}
\end{itemize}

@@

\item Open Atom and a new file. 
\begin{itemize}
\item In a similar fashion as above, create a {\tt .csv } file with the following information separated by commas
\begin{itemize}
\item Expected major (or concentration)
\item Scale of 1-5 (5 being a lot, 1 being none) experience with programming
\item preferred form of social media
\item career path (e.g. Finance, Consulting, Technology, Fashion, public policy, rock star)
\end{itemize}
\item Name as \verb|my_second_file.csv| and post on GitHub in \verb|my_first_repository|
\end{itemize}

>>>>

@@

\item Environments
\begin{itemize}
\item Environments?  (Analogy:  Word is an environment for creating Word docs.)
\item Jupyter:  environment for creating IPython notebooks, which combine code with text and output
\end{itemize}
\end{itemize}

@@

\needspace{2\baselineskip}
\item Run test program in Jupyter Notebook
\begin{itemize}
\item Put red sticker on your laptop
\item From Terminal/Command prompt type \verb|jupyter notebook|
\item Look around...
\item Enter test program in a code cell
\item Click on \verb|Untitled| and rename the file as \verb|bootcamp_test|
\item Click on save button
\item Click on code cell, press \verb|shift + enter|
\item Look for correct output (last line should be {\tt 3.6.x etc})
\item Switch to green sticker if it works
\end{itemize}

@@

\item Jupyter Notebook startup summary
\begin{itemize}
\item Open Terminal/Command and type \verb|jupyter notebook|
\end{itemize}
\end{itemize}

\section*{\href{https://github.com}{GitHub}}
\begin{itemize}
\item What I will use it for\ldots
\begin{itemize}
\item Source of ALL course materials
\item Place for you to grab materials on the fly. Save files by cut and paste, clever save as, or "Raw" (ask about this)
\end{itemize}
\item You need to create an account and email me your username
\item What you will use it for\ldots
\begin{itemize}
\item Think of this like an artists portfolio. Here you can post your code and projects and show potential employers, family, friends what you have done.
\end{itemize}
\item Now lets use it
\begin{itemize}
\item Put red sticker on your laptop
\item Sign into github (if you do not have an account, create one)
\item Create a new repository and name it \verb|my_first_repository|,
\item place the \verb|my_first_file.csv| file you created in it,
\item Great job! Replace red sticker with green!\\
Next class, I'm going to try and ``pull'' the file and then report some statistics about the class to you.
\end{itemize}
\end{itemize}

@@
